Learning and comparing functional connectomes between populations

### 2012-12-26 paper.tex
Iter on paper

%{{{------ Inter subject fluctuations ----------------------------------------
\begin{figure}
\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.17\linewidth}{%
	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small Covariance matrices}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!4\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small Z score on difference}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!4\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small Z score on residuals \scriptsize
		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
	}%
    \hspace*{.993\linewidth}%
}

\caption{Inter subject fluctuations
\label{fig:icov_regressors}
}
\end{figure}
%---------------------------------------------------------------------------}}}

\paragraph{Modeling between-connection dependences}

Show that correlations co-fluctuation with images, spatial correlations between correlations.

Ad-hoc model: network-based statistics \cite{zalesky2010}

Discuss the 'residual' strategy?
\cite{varoquaux2010b}

@@

Small world networks, transport properties, resilient...

Warning note that correlation matrices have long-tailed degree
distribution by definition (cite recent Bullmore paper showing that).

@@

>>>>

%{{{------ Inter subject fluctuations ----------------------------------------
\begin{figure}
\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.17\linewidth}{%
	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{a}. Correlation matrices}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{b}. Z score on difference}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.17\linewidth}{%
	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{c}. Inverse-covariance matrices}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{d}. Z score on inverse-covariance}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub00.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub29.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub01.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub07.pdf}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub53.pdf}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{e}. Z score on residuals \scriptsize
		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
	}%
    \hspace*{.993\linewidth}%
}

\caption{Inter subject variability. Note that this is variability
occurring in a healthy population at rest, in other words non specific
variability -- \textbf{a}: single-subject
correlation matrices for different subjects -- \textbf{b}:
Corresponding Z-score (effect / standard deviation) of the difference
between a subject and the remaining others -- \textbf{c}:
single-subject precision matrices -- \textbf{d}: Corresponding Z-score
for the precision matrices -- \textbf{e}:
Corresponding Z-score for the subject residuals, as defined in 
\cite{varoquaux2010b}.
\label{fig:inter_subject}}
\end{figure}
%---------------------------------------------------------------------------}}}

\paragraph{Accounting for distributed variability}
%
A specific challenge of connectivity analysis is that the connectivity
between different regions tend to covary. For instance, with
resting-state data, functional networks comprising many nodes can appear
as more or less connected across subjects (see for instance
Fig.\,\ref{fig:inter_subject}.a, showing variability in a control
population at rest). In other words, non-specific variability is
distributed accross the connectivity graph, and it is structured by the
graph itself. This observation brings the natural question of whether
second-level analysis should be performed on correlation matrices,
inverse-covariance matrices, or another parametrisation that would
disentangle effects and give unstructured (white) residuals. While
inverse-covariance matrices show less distributed fluctuations than
correlation matrices, they capture a lot of background noise, as partial
correlations are intrinsically harder to estimate. Preliminary work
\cite{varoquaux2010b} suggest to perform statistics on residuals of
a parametrisation intermediate between correlation matrix and inverse
covariance matrix.

Taking a difference stance on distributed variability, the ``network-based
statistics'' approach \cite{zalesky2010} draws from the hypothesis that
if, in a second-level analysis, an effect is detected in a connection
that lies in a network of strongly connected nodes, the whole network is
likely to cary an effect. Thus, they adapt cluster-level inference to
connectivity analysis, in order to mitigate the curse of multiple
comparisons.

@@

@@

Small world networks, transport properties, resilient...
\cite{achard2006,bullmore2009}

Warning note that correlation matrices have long-tailed degree
distribution by definition \cite{zalesky2012}.
